
---
title: "Untitled"
author: "Nina Vu"
date: "7/15/2020"
output: html_document
---

#Obtain

 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Obtaining SBUX and DNKN from Yahoo

First, I have to obtain Statrbuck and Dunkin Brand stock data. Using the getSymbols function, I was able to get the stock information from the begining of this year up until now. 
```

getSymbols(Symbols = c("DNKN", "SBUX"), src = "yahoo", from = "2020-01-01", to = Sys.Date(), auto.assign = TRUE)

```
## Obtaining the price of sugar and coffee base on continuos contract from Quandl
```{r}
#Price of Sugar
Sugar_Contract <- Quandl(code = "CHRIS/ICE_SB1", start_date = "2020-01-01", api_key = "uZELH75uxUZH1ck7iNPF")
Sugar_Contract <- mutate(Sugar_Contract, Name = "Sugar")
Sugar_Contract <- select(Sugar_Contract, Date, Open, Name)
Sugar_Contract <- rename(Sugar_Contract, Value = Open)

#Price of coffee
Coffee_Contract <- Quandl(code = "CHRIS/ICE_KC5", start_date = "2020-01-01", api_key = "uZELH75uxUZH1ck7iNPF")
Coffee_Contract <- mutate(Coffee_Contract, Name = "Coffee")
Coffee_Contract <- select(Coffee_Contract, Date, Open, Name)
Coffee_Contract <- rename(Coffee_Contract, Value = Open)

```
## Since the form of stock data on Yahoo is not in the same format as the data on Quandl. I have to convert it using tibble

```{r}
SBUX_tibble <- as_tibble(SBUX)
SBUX_tibble <- mutate(SBUX_tibble, Date = index(SBUX))
SBUX_tibble <- mutate(SBUX_tibble, Name = "Starbuck")
SBUX_tibble <- select(SBUX_tibble, Date, SBUX.Close, Name)
SBUX_tibble <- rename(SBUX_tibble, Value = SBUX.Close)


DNKN_tibble <- as_tibble(DNKN) 
DNKN_tibble <- mutate(DNKN_tibble, Date = index(DNKN))
DNKN_tibble <- mutate(DNKN_tibble, Name = "Dunkin")
DNKN_tibble <- select(DNKN_tibble, Date, DNKN.Close, Name)
DNKN_tibble <- rename(DNKN_tibble, Value = DNKN.Close)

```
## The last step in processing the data is to combine them

```{r}

#Combine all Data
all_data <- rbind(SBUX_tibble, DNKN_tibble, Sugar_Contract, Coffee_Contract)

```






